### 2016-09-21 doc/publications/plos16/plos16.tex
Added data for performnce and scalability section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 1:  Feature selection 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CursedForest grows denser forests to stabilise feature importance ranking}
In this section we demonstrate that \cursedforest 's ability to rapidly grow large number of trees, \texttt{ntree}, in parallel results in a stable feature importance ranking.
This concept was originally proposed by Liaw and Weiner~\cite{Liaw.and.Weiner.2002}, who suggested that though the variable importance measures may vary from run to run, the ranking of the variables will stabilise with growing \texttt{ntree}.

To investigate this hypothesis for data sets with large number of feature variables we generated a synthetic dataset ...

@@

\begin{table}[!ht]
\centering
\caption{
{\bf Time in seconds to build random forest with 100
  trees with specified mtry fraction using given number of CPU cores.}}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{\multirow{2}{*}{}}                   & \multicolumn{4}{|c|}{Number of CPU cores}  \\
                                                            &  & 16   & 32      & 64      & 128  \\
\multirow{3}{*}{mtry (fraction)}                     & 0.10 & 708.27  & 340.00  & 186.01 & 134.47 \\	
                                                     & 0.25 & 1134.89 & 535.01  & 270.78 & 179.59 \\	
                                                     & 0.80 & 2313.47 & 1125.70 & 569.10 & 346.58 \\	
\hline
\end{tabular}
\begin{flushleft} 
\end{flushleft}
\label{table10}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 1:  Feature selection 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CursedForest performance and scalability}
%In this section we demonstrate that \cursedforest 's ability to rapidly grow large number of trees, \texttt{ntree}, in parallel results in a stable feature importance ranking.
%This concept was originally proposed by Liaw and Weiner~\cite{Liaw.and.Weiner.2002}, who suggested that though the variable importance measures may vary from run to run, the ranking of the variables will stabilise with growing \texttt{ntree}.

%To investigate this hypothesis for data sets with large number of feature variables we generated a synthetic dataset ...

\begin{table}[!ht]
\centering
\caption{
{\bf Time in seconds to build random forest of 100
  trees with specified mtry fraction using given number of CPU cores.}}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{\multirow{2}{*}{}}                   & \multicolumn{4}{|c|}{Number of CPU cores}  \\
                                                            &  & 16   & 32      & 64      & 128  \\
\multirow{3}{*}{mtry (fraction)}                            & 0.10 & 708.3  & 340.0  & 186.0 & 134.5 \\
                                                            & 0.25 & 1134.9 & 535.0  & 270.8 & 179.6 \\
                                                            & 0.50 & 1724.1 & 856.6  & 428.7 & 243.8 \\
                                                            & 0.80 & 2313.5 & 1125.7 & 569.1 & 364.6 \\

\hline
\end{tabular}
\begin{flushleft} 
\end{flushleft}
\label{table10}
\end{table}

\begin{figure}[tbhp]
\begin{tabular}{ll}
a)& b)\\
\includegraphics[totalheight=6cm]{./figs/mtry_cpu.png} & 
\includegraphics[totalheight=6cm]{./figs/cpu_mtry_trees_per_hour.png} \\
\end{tabular}
\captionof{figure}{{\bf Scalablity of the Wide Random Forest on the synthetic dataset of 2.5M features and 5K samples.} 
   {\bf a)} Time in seconds to build 100 trees for differnet mtry fractions. 
   {\bf b)} Number of trees build per hour when using a growing number of CPU cores.}
\label{figure:synth}
\end{figure}

@@
